Technical Report

### 2017-12-20 fully-abstract-comp/technical-report.tex
updated K-rel
updated K-rel
mend
Some more minor updates to the op sem. Please read the new question under interpretation of call.

\noindent\textbf{xjmp}\\
\lau{22-09-2017: Can we allow the callee to return any stack pointer? At the moment, it is not possible to create an empty stack pointer which may be a saving grace. If we at some point change this, so you can split capabilities into empty ones, then we need to consider whether it is safe for callees to return empty stacks (I think it is okay as long as we always have some stack usage).}
\lau{28-09-2017: For now, the jump to a return pointer does the stack end point check. We could possibly move this to the proposed semantic condition as well.}
\begin{align*}
  \sem{\txjmp{r_1}{r_2}}(\Phi) = &
                                   \begin{cases}
                                     \arraycolsep=0pt
                                     \begin{array}[t]{rl}
                                       \Phi & \updReg{r_1}{w_1}\\
                                            & \updReg{r_2}{w_2}\\
                                            & \updReg{\pcreg}{c_\code}\\
                                            & \updReg{\rdata}{c_\data}
                                     \end{array} &
                                     \begin{array}[t]{l}
                                       \Phi(r_1) = \sealed{\sigma,c_\code} \tand \\
                                       \Phi(r_2) = \sealed{\sigma,c_\data} \tand \\
                                       \nonExec{c_\data} \tand \\
                                       w_1 = \linCons{\Phi(r_1)} \tand \\
                                       w_2 = \linCons{\Phi(r_2)}
                                     \end{array}
                                     \\&\\
                                     \sourcecolor\left.
                                       \arraycolsep=0pt
                                       \begin{array}[t]{rl}
                                         \Phi' & \updReg{r_2}{0} \\
                                               & \updReg{\pcreg}{\opc}\\
                                               & \updReg{\rdata}{0}\\
                                               & \updReg{\rstk}{c_\stk}
                                       \end{array}\right.&
                                     \sourcecolor\left.
                                       \begin{array}[t]{l}
                                         \Phi(r_1) = \retptrc(\sigma,\_) \tand \\
                                         \Phi(r_2) = \retptrd(\sigma,(\aaddr_\stk,\_)) \tand \\
                                         \Phi(\rstk) = \stkptr{\rw,\stkb,\eaddr_\stk,\_} \tand \\
                                         \Phi = (\mem,\reg,\stkf::\stk,\ms_\stk) \tand \\
                                         \stkf = (\opc,\ms_{\stk,\priv}) \tand \\
                                         \dom(\ms_{\stk,\priv}) = [\eaddr_\stk+1,\eaddr_{\stk,\priv}] \tand\\
                                         c_\stk = \stkptr{\rw,\stkb,\eaddr_{\stk,\priv},\aaddr_\stk} \tand\\
                                         \Phi' = (\mem,\reg,\stk,\ms_{\stk,\priv} \uplus \ms_\stk) 
                                       \end{array}\right.
                                     \\
                                     \failed & \totherwise
                                   \end{cases}
\end{align*}

@@

This instruction assumes that the current address of the stack pointer, $\aaddr_\stk$, points to the first free address of the stack. We assume a seal assignment function $\sealAss{}$ that given an address assigns a seal.\lau{25-09-2017: This will need some more explanation - namely, there should be some relationship between the available seals and this function (I also need to think more about the specifics of this).}

@@

                                                        &\updReg{\rretd}{\retptrd(\sigma_?,(\aaddr_\stk,\eaddr_\stk))}

@@

                                                   c_\stk = \stkptr{\baddr_\stk,\aaddr_\stk-1,\aaddr_\stk-1} \tand \\

@@

                                                   \mem(\baddr) = \seal{\sigma_\baddr,\sigma_\eaddr,\sigma_\baddr}\tand\\

@@

                                                   \sigma_? = \sealAss{a} \tand\\

@@

@@

\[
  \begin{array}{rl}
  \lrk(W) = &\left\{ \npair{\left(\array{l}\src{\retptrc(\sigma,(\perm,\lin,\baddr_c,\eaddr_c,\aaddr_c))},\\\src{\retptrd(\sigma,(\aaddr_d,\eaddr_d))},\\k_{c,T},k_{d,T}\endarray\right)} \middle|
    \begin{array}{l}
      k_{d,T} = \sealed{\sigma,c_d} \wedge\\
      k_{c,T} = \sealed{\sigma,c_c} \wedge\\
      c_c = ((\perm,\lin),\baddr_c,\eaddr_c,\aaddr_c) \wedge\\
      c_d = ((\rw,\linear),\aaddr_d,\eaddr_d,\aaddr_d-1) \wedge\\
      \npair[n]{[\stpair[.]{\retptrc(\sigma,\_)}{k_{c,T}},\stpair[.]{\retptrd(\sigma,\_)}{k_{d,T}}]} \in \lrp(W) \wedge \\
      \forall n' \leq n, W' \pubft W \ldotp \\
      \quad \forall W_\lrr, W_\lrm \ldotp  \\
      \qquad\memSat[n']{\stpair[.]{\ms_S,(\opc,\ms_{\stk,f}) :: \stk,\ms_\stk}{\ms_T}}{W_\lrm} \wedge \\
      \qquad\opc = c_c \wedge\\
      \qquad\dom(\ms_{\stk,f}) = [\aaddr_d,\eaddr_d] \wedge\\
      \qquad\npair[n']{\left(\array{l}\src{\reg_S\update{\rstk}{\stkptr{\rw,\stkb,\eaddr_d,\aaddr_d}}},\\
                               {\reg_T\update{\rstk}{((\rw,\linear),\stkb,\eaddr_d,\aaddr_d)}}\endarray \right)}\in \lrr(\{r_\stk\})(W_\lrr) \wedge\\ 
      \qquad\npair[n']{[(\opc,\opc)]} \in \lrp(W')\\
      \qquad\Rightarrow\\
      \qquad \npair[n']{\left(\arraycolsep=0pt\array{l}
                          \left(\arraycolsep=0pt\array{l}
                            \src{\ms_S,\reg_S\update{\pcreg,\rstk}{\opc,\stkptr{\rw,\stkb,\eaddr_d,\aaddr_d}},}\\
                            \src{\stk, \ms_\stk \uplus \ms_{\stk,f}}
                          \endarray \right) \\
                          \left(\ms_T,\reg_T\update{\pcreg,\rstk}{\opc,((\rw,\linear),\stkb,\eaddr_d,\aaddr_d)} \right)
                        \endarray \right)} \in \lro(W'\oplus W_\lrr \oplus W_\lrm)
    \end{array}
  \right\}
% \\ \cup
%     & \left\{ \npair{\left( k_{c,S},k_{d,S},k_{c,T},k_{d,T} \right)} \middle|
%       \begin{array}{l}
%         \pi_\sigma(k_{c,S}) = \pi_\sigma(k_{d,S}) \wedge \pi_\sigma(k_{c,T}) = \pi_\sigma(k_{d,T}) \wedge \npair{(k_{c,S},k_{c,T}),(k_{d,S},k_{d,T})} \in \lrp(W) \\
%         \forall n' \leq n, W' \pubft W \ldotp \\
%         \quad \npair[n']{(k_{c,S},k_{c,T}),(k_{d,S},k_{d,T})} \in \lrp(W) \Rightarrow\\
%         \qquad \forall \npair[n']{\stpair{\reg}{\reg}} \in \lrr(\{\rdata\})(W'_\lrr) \ldotp 
%                \forall \memSat[n']{\src{\ms_S,\stk,\ms_\stk},\ms_T}{W'_\lrm} \ldotp\\
%         \qquad \quad \npair[n']{\left(
%         \arraycolsep=0pt\array{l}
%           (\src{\ms_S},\src{\reg_S}\update{\pcreg,\rdata}{\pi_\vsc(\src{k_{c,S}}),\pi_\vsc(\src{k_{d,S}})},\src{\stk},\src{\ms_\stk}),\\
%           (\ms_T,\reg_T\update{\pcreg,\rdata}{\pi_\vsc(k_{c,T}),\pi_\vsc(k_{d,T})})
%         \endarray\right)} \in \lro(W' \oplus W'_\lrr \oplus W'_\lrm)
%       \end{array}
%      \right\}
  \end{array}
\]

>>>>

\noindent\textbf{xjmp}\\
\lau{22-09-2017: Can we allow the callee to return any stack pointer? At the moment, it is not possible to create an empty stack pointer which may be a saving grace. If we at some point change this, so you can split capabilities into empty ones, then we need to consider whether it is safe for callees to return empty stacks (I think it is okay as long as we always have some stack usage).}
\lau{28-09-2017: For now, the jump to a return pointer does the stack end point check. We could possibly move this to the proposed semantic condition as well.}
\begin{align*}
  \sem{\txjmp{r_1}{r_2}}(\Phi) = &
                                   \begin{cases}
                                     \arraycolsep=0pt
                                     \begin{array}[t]{rl}
                                       \Phi & \updReg{r_1}{w_1}\\
                                            & \updReg{r_2}{w_2}\\
                                            & \updReg{\pcreg}{c_\code}\\
                                            & \updReg{\rdata}{c_\data}
                                     \end{array} &
                                     \begin{array}[t]{l}
                                       \Phi(r_1) = \sealed{\sigma_1,c_\code} \tand \\
                                       \Phi(r_2) = \sealed{\sigma_2,c_\data} \tand \\
                                       \sigma_1 = \sigma_2 \tand \\
                                       \nonExec{c_\data} \tand \\
                                       w_1 = \linCons{\Phi(r_1)} \tand \\
                                       w_2 = \linCons{\Phi(r_2)}
                                     \end{array}
                                     \\&\\
                                     \sourcecolor\left.
                                       \arraycolsep=0pt
                                       \begin{array}[t]{rl}
                                         \Phi' & \updReg{r_2}{0} \\
                                               & \updReg{\pcreg}{\opc}\\
                                               & \updReg{\rdata}{0}\\
                                               & \updReg{\rstk}{c_\stk}
                                       \end{array}\right.&
                                     \sourcecolor\left.
                                       \begin{array}[t]{l}
                                         \Phi(r_1) = \retptrc(\sigma_1,\_) \tand \\
                                         \Phi(r_2) = \retptrd(\sigma_2,(\aaddr_\stk,\_)) \tand \\
                                         \sigma_1 = \sigma_2 \tand\\
                                         \Phi(\rstk) = \stkptr{\rw,\stkb,\eaddr_\stk,\_} \tand \\
                                         \Phi = (\mem,\reg,\stkf::\stk,\ms_\stk) \tand \\
                                         \stkf = (\opc,\ms_{\stk,\priv}) \tand \\
                                         \dom(\ms_{\stk,\priv}) = [\eaddr_\stk+1,\eaddr_{\stk,\priv}] \tand\\
                                         c_\stk = \stkptr{\rw,\stkb,\eaddr_{\stk,\priv},\aaddr_\stk} \tand\\
                                         \Phi' = (\mem,\reg,\stk,\ms_{\stk,\priv} \uplus \ms_\stk) 
                                       \end{array}\right.
                                     \\
                                     \failed & \totherwise
                                   \end{cases}
\end{align*}

@@

\lau{20-12-2017: At some point, I added an offset annotation $o$ to all calls. I believe this removes the need for a function that annotate seals. It will still have to be checked that all calls in a program uses different offsets, but I suspect this can be done as some assumption in what we want to prove.}
\lau{20-12-2017: Until this day, we had a $\sealAss{}$ function: This instruction assumes that the current address of the stack pointer, $\aaddr_\stk$, points to the first free address of the stack. We assume a seal assignment function $\sealAss{}$ that given an address assigns a seal.\lau{25-09-2017: This will need some more explanation - namely, there should be some relationship between the available seals and this function (I also need to think more about the specifics of this).}}

@@

                                                        &\updReg{\rretd}{\retptrd(\sigma_?,(\aaddr_\stk,\eaddr_\stk))}\\
                                                        &\updReg{\rtmp{1}}{0}

@@

                                                   c_\stk = \stkptr{\rw,\baddr_\stk,\aaddr_\stk-1,\aaddr_\stk-1} \tand \\

@@

                                                   \mem(\baddr) = \seal{\sigma_\baddr,\sigma_\eaddr,\sigma_\aaddr}\tand\\
                                                   \sigma_? = \sigma_\aaddr + o \tand\\

@@

@@

\lau{20-12-2017: After looking this over, I have a couple of questions (for myself and everyone else): In the condition for call, we assume $\Phi(\rstk) = \stkptr{\rw,\baddr_\stk,\eaddr_\stk,\aaddr_\stk}$. There is, however, no check in the implementation of call that ensures this. That says, we are going to have an assumption that the stack pointer base address has been checked before all calls (i.e., that it is $\stkb$) which would indeed mean that it is a stack pointer (assuming that the address $\stkb$ is a stack address to begin with). Why did we not want to check the stack end address here? And if we do not check it as part of the call implementation, do we then want to match the call implementation better?}

@@

\[
  \begin{array}{rl}
  \lrk(W) = &\left\{ \npair{\left(\array{l}\src{\retptrc(\sigma,(\perm,\lin,\baddr_c,\eaddr_c,\aaddr_c))},\\\src{\retptrd(\sigma,(\aaddr_d,\eaddr_d))},\\k_{c,T},k_{d,T}\endarray\right)} \middle|
    \begin{array}{l}
      k_{d,T} = \sealed{\sigma,c_d} \wedge\\
      k_{c,T} = \sealed{\sigma,c_c} \wedge\\
      c_c = ((\perm,\lin),\baddr_c,\eaddr_c,\aaddr_c) \wedge\\
      c_d = ((\rw,\linear),\aaddr_d,\eaddr_d,\aaddr_d-1) \wedge\\
      \npair[n]{[\stpair[.]{\retptrc(\sigma,\_)}{k_{c,T}},\stpair[.]{\retptrd(\sigma,\_)}{k_{d,T}}]} \in \lrp(W) \wedge \\
      \forall n' \leq n, W' \pubft W \ldotp \\
      \quad \forall W_\lrr, W_\lrm \ldotp  \\
      \qquad\memSat[n']{\stpair[.]{\ms_S,(\opc,\ms_{\stk,f}) :: \stk,\ms_\stk}{\ms_T}}{W_\lrm} \wedge \\
      \qquad\opc = ((\perm,\lin),\baddr_c,\eaddr_c,\aaddr_c+12) \wedge\\
      \qquad\dom(\ms_{\stk,f}) = [\aaddr_d,\eaddr_d] \wedge\\
      \qquad\npair[n']{\left(\array{l}\src{\reg_S\update{\rstk}{\stkptr{\rw,\stkb,\eaddr_d,\aaddr_d}}},\\
                               {\reg_T\update{\rstk}{((\rw,\linear),\stkb,\eaddr_d,\aaddr_d)}}\endarray \right)}\in \lrr(\{r_\stk\})(W_\lrr) \wedge\\ 
      \qquad\npair[n']{[(\opc,\opc)]} \in \lrp(W')\\
      \qquad\Rightarrow\\
      \qquad \npair[n']{\left(\arraycolsep=0pt\array{l}
                          \left(\arraycolsep=0pt\array{l}
                            \src{\ms_S,\reg_S\update{\pcreg,\rstk}{\opc,\stkptr{\rw,\stkb,\eaddr_d,\aaddr_d}},}\\
                            \src{\stk, \ms_\stk \uplus \ms_{\stk,f}}
                          \endarray \right) \\
                          \left(\ms_T,\reg_T\update{\pcreg,\rstk}{\opc,((\rw,\linear),\stkb,\eaddr_d,\aaddr_d)} \right)
                        \endarray \right)} \in \lro(W'\oplus W_\lrr \oplus W_\lrm)
    \end{array}
  \right\}
% \\ \cup
%     & \left\{ \npair{\left( k_{c,S},k_{d,S},k_{c,T},k_{d,T} \right)} \middle|
%       \begin{array}{l}
%         \pi_\sigma(k_{c,S}) = \pi_\sigma(k_{d,S}) \wedge \pi_\sigma(k_{c,T}) = \pi_\sigma(k_{d,T}) \wedge \npair{(k_{c,S},k_{c,T}),(k_{d,S},k_{d,T})} \in \lrp(W) \\
%         \forall n' \leq n, W' \pubft W \ldotp \\
%         \quad \npair[n']{(k_{c,S},k_{c,T}),(k_{d,S},k_{d,T})} \in \lrp(W) \Rightarrow\\
%         \qquad \forall \npair[n']{\stpair{\reg}{\reg}} \in \lrr(\{\rdata\})(W'_\lrr) \ldotp 
%                \forall \memSat[n']{\src{\ms_S,\stk,\ms_\stk},\ms_T}{W'_\lrm} \ldotp\\
%         \qquad \quad \npair[n']{\left(
%         \arraycolsep=0pt\array{l}
%           (\src{\ms_S},\src{\reg_S}\update{\pcreg,\rdata}{\pi_\vsc(\src{k_{c,S}}),\pi_\vsc(\src{k_{d,S}})},\src{\stk},\src{\ms_\stk}),\\
%           (\ms_T,\reg_T\update{\pcreg,\rdata}{\pi_\vsc(k_{c,T}),\pi_\vsc(k_{d,T})})
%         \endarray\right)} \in \lro(W' \oplus W'_\lrr \oplus W'_\lrm)
%       \end{array}
%      \right\}
  \end{array}
\]
